Video-Agnostic Perturbation: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-13 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
更新 related work

PAT generated physical adversarial textures visa white-box attack to let the tracker lock on the texture when a tracked object moves in front of it. However, PAT validates its method by attacking a light deep regression tracker, i.e., GOTURN that has low tracking accuracy on modern benchmarks. In this paper, we aim to attack the state-of-the-art trackers

>>>>

RTAA \cite{RTAA} takes temporal motion into consideration when generating lightweight perturbations over the estimated tracking results frame-by-frame. However, RTAA only performs the untargeted attack for tarckers, which causes the adversarial trajectory to deviate from the original trajectory of an object. In this paper, we focus on the more challenging targeted attack for object tracking.

PAT generated physical adversarial textures visa white-box attack to let the tracker lock on the texture when a tracked object moves in front of it. However, PAT validates its method by attacking a light deep regression tracker, i.e., GOTURN that has low tracking accuracy on modern benchmarks. In this paper, we aim to attack the state-of-the-art trackers based on the Siamese networks.
